Eine Einführung in R für die sozioökonomische Forschung

### 2019-10-17 Chap-visualization.Rmd
Add #> as output sign

@@

<img src="../figures/chart-selection.png" alt="drawing" width="600"/>

  Source: [eazybi.com](https://eazybi.com/blog/data_visualization_and_chart_types/)

>>>>

```{r include=FALSE}
knitr::opts_chunk$set(comment = "#>")
```

@@

```{r, echo=FALSE, fig.align='center', out.width='80%', fig.cap="Source: [eazybi.com](https://eazybi.com/blog/data_visualization_and_chart_types/)"}
knitr::include_graphics("figures/figures/chart-selection.png")
```
